Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-05-17 PaperBCJ.tex
Dataset

\section{Matherial and Methods}
%Codigo para la Implementacion del Algoritmo

@@

%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
 \bibitem{Cicco:Potena}
 M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.
\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

\section{Matherial and Methods}
%Codigo para la Implementacion del Algoritmo
Dataset Desciption:
\\
For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of 2000 images, of which 1600 images were used for the training and 400 for the validation, once obtained the images are processed by openCV to segment them and can be obtained as follows:
\\
\includegraphics[width=3in]{im1}\\[1ex]

@@

%Poner Bibliografia Correcta, Revisar si es neceario poner cuatro nombres  
 \bibitem{Cicco:Potena}
 M.~Di Cicco, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{Automatic Model  Based Dataset Generation for Fast and Accurate Crop and Weeds Detecion} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
